--- 
title: "Elegant Bookdown Template"
subtitle: "优雅的 Bookdown 书籍模版"
author: 
  - 黄湘云
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: elegantbook
bibliography: 
 - book.bib
 - packages.bib
lot: yes
lof: yes
colorlinks: yes
link-citations: yes
github-repo: XiangyunHuang/ElegantBookdown
classoption: "cn,11pt,chinese,bibstyle=apalike"
description: "This is a bookdown template based on ElegantBook. The output format for this template is bookdown::gitbook and bookdown::pdf_book."
---

\mainmatter

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE,cache=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
